\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

% Sections
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule\vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{
  {#1 \vspace{-2pt}}
}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

%----------Header-----------------
\begin{center}
	{\Huge \scshape Shenghan Gao} \\ \vspace{1pt}
	Ann Arbor, MI • \href{mailto:shenghan@umich.edu}{shenghan@umich.edu} • +86 15800522128 (China)\\
	\href{https://github.com/gaoshenghan1130}{https://github.com/gaoshenghan1130} \\
	\small{Eligible to work in the US under CPT authorization}
\end{center}

%-----------Education-----------------
\section{Education}
\resumeSubHeadingListStart
\item
\textbf{University of Michigan – Shanghai Jiao Tong University Joint Institute} \\
\makebox[\textwidth][r]{\textit{Ann Arbor, MI / Shanghai, China}} \\
\textit{Bachelor of Science in Engineering} \\
\textit{Dual Degree: Mechanical Engineering and Electrical \& Computer Engineering} \hfill \textit{Expected May 2027} \\
\small{CPT-eligible international student (F-1) studying in the U.S. from Sep 2025 to May 2027}
\resumeSubHeadingListEnd

%-----------Skills-----------------
\section{Skills}
\begin{tabularx}{\textwidth}{l X}
	Languages:  & C++, Python, Lua, CMake, Protobuf, SQL, MATLAB, C\#, Java, Elm \\
	Frameworks: & Qt, Arduino, Unity, .NET Core                                  \\
	Tools:      & Git, VS Code, NeoVim, Mathematica, SolidWorks                  \\
\end{tabularx}

%-----------Projects-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
{Multi-Agent Role Assignment and Coordination}{Nov 2023}
{Team Project – SJTU RoboCup Team}{}
\resumeItemListStart
\resumeItem{Designed and implemented real-time multi-agent role assignment using the Munkres (Hungarian) algorithm to optimize spatial task allocation during dynamic gameplay.}
\resumeItem{Used Ferrari’s method in C++ to solve a quartic equation arising from time-to-target estimation, enabling real-time cost matrix construction for Munkres-based task assignment.}
\resumeItem{Built modular interfaces with finite state machines to support flexible role switching under changing environmental constraints, contributing to adaptive team strategy.}
\resumeItemListEnd



\resumeSubheading
{Obstacle Avoidance and Motion Planning System}{Dec 2023 – Mar 2024}
{Team Project – SJTU RoboCup Team}{}
\resumeItemListStart
\resumeItem{Developed modular path planning systems based on D* and DWA algorithms for dynamic, partially known environments.}
\resumeItem{Constructed simulation-based testing pipelines to evaluate performance under uncertainty and latency constraints.}
\resumeItem{Integrated the planning module with low-level motion controllers and perception subsystems for real-time operation.}
\resumeItem{Collaborated with hardware and control teams to ensure safe trajectory execution, bridging software and physical systems.}
\resumeItemListEnd


\resumeSubheading
{Remote-Controlled Pickup Robot – LiMing Cup Mechanical Innovation Competition}{Mar 2024 – May 2024}
{Team Project – SJTU Innovation Association}{}
\resumeItemListStart
\resumeItem{Designed and implemented a mechanical arm for a remote-controlled robot to pick up and place blocks efficiently in a competitive arena.}
\resumeItem{Programmed multi-threaded control logic on Arduino to manage coordinated movement between arm joints, gripper, and drive system.}
\resumeItem{Integrated sensor inputs (limit switches, encoders) to support responsive control and avoid mechanical interference.}
\resumeItem{Collaborated with mechanical and electrical teammates on the design and tuning of actuators, transmission mechanisms, and control layout.}
\resumeItem{Received the \textbf{Best Design Award} at the 14th LiMing Cup among over 50 teams, recognized for system reliability and mechanical innovation.}
\resumeItemListEnd

\resumeSubheading
{UDP Server for Cross-Language Module Integration}{Sep, 2024}
{Team Project – SJTU RoboCup Team}{}
\resumeItemListStart
\resumeItem{Developed an independent UDP server in Python to enable external Python modules (e.g., PyTorch) to communicate with a legacy C++/Lua-based system.}
\resumeItem{Designed and implemented a communication protocol using Protocol Buffers (protobuf), with supporting scripts in C++ and Python; features include one-sided disconnection handling, automatic reconnection, and multi-type data transmission.}
\resumeItem{Asynchronously handled multiple client connections using Python’s \texttt{asyncio} and Qt’s signals and slots, enabling efficient data exchange between the server and multiple clients.}
\resumeItem{Wrapped the Qt \texttt{QProcess} class to store static return values, allowing update functions to directly access returned data.}
\resumeItem{Utilized Python’s \texttt{multiprocessing} to assign independent processes for computation tasks, achieving multicore utilization; implemented file pipes for parameter updates and shared memory for data exchange.}
\resumeItem{Built a simple UI to monitor the status of active tasks.}
\resumeItemListEnd


% \resumeSubheading
% {Unity Game Design and Development}{Oct, 2024}
% {Personal Project}{}
% \resumeItemListStart
% \resumeItem{Designed and developed a 3D game in Unity, focusing on game mechanics, level design, and user interface implementation.}
% \resumeItem{Implemented game logic and features using C\#, including player controls and scoring systems.}
% \resumeItem{Gained familiarity with Mono/.NET framework for Unity to support cross-platform development.}
% \resumeItemListEnd
%
% \resumeSubheading
% {Precise Test Functions for Skills and Controls in SRC Robots}{2024}
% {Team Project – SJTU RoboCup Team}{}
% \resumeItemListStart
% \resumeItem{Rewrote the singleton system to support CRTP (Curiously Recurring Template Pattern) for enhanced type safety and compile-time validation.}
% \resumeItem{Implemented a scoring system by wrapping the existing debug engine to display structured scoreboards, replacing scattered print statements.}
% \resumeItem{Developed a suite of motion control test functions (as templates), specifically targeting D* Lite path planning algorithms.}
% \resumeItemListEnd


% \resumeSubheading
% {2D Interactive Game Development with Elm}{May, 2024}
% {Team Project – SJTU}{}
% \resumeItemListStart
% \resumeItem{Implemented a custom physics engine for the game, including collision detection, gravity, friction, momentum, and energy conservation.}
% \resumeItem{Optimized the original \textit{Messenger} structure, improving collision detection performance for brick-like objects by a factor of $10^{3}$.}
% \resumeItem{Managed complex UI interactions and game state using Elm’s The Elm Architecture (TEA), ensuring smooth gameplay and responsiveness.}
% \resumeItem{Enhanced browser performance to achieve low latency and seamless user experience.}
% \resumeItemListEnd


% \resumeSubheading
% {Cross-Platform UI Application with JavaScript, Swing, and MySQL}{2023}
% {Personal Project}{}
% \resumeItemListStart
% \resumeItem{Developed a desktop application with JavaScript and Swing for the user interface, ensuring responsive and intuitive UX.}
% \resumeItem{Implemented MySQL database backend for persistent data storage and efficient data retrieval.}
% \resumeItem{Designed and integrated seamless communication between frontend UI and backend database.}
% \resumeItemListEnd
%

\resumeSubHeadingListEnd

%-----------Experience-----------------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Software Team Leader – SJTU RoboCup Team}{Sep 2024 – Present}
{Shanghai Jiao Tong University}{}
\resumeItemListStart
\resumeItem{Led a 20-member software team in developing and maintaining the RoboCup Small Size League (SSL) system.}
\resumeItem{Reconstructed the CMake build system to simplify project structure and significantly improve compilation speed.}
\resumeItem{Initiated cross-platform compatibility across Windows, Linux, and macOS to streamline team collaboration.}
\resumeItem{Collaborated closely with the hardware team to optimize motion control and improve both offensive and defensive strategies.}
\resumeItem{Oversaw integration of multi-language codebases (C++, Lua, Python) with a focus on modularity and real-time performance.}
\resumeItem{Made key architectural decisions, including replacing \texttt{pybind11} with a custom UDP server for cross-language module integration.}
\resumeItem{Served as the final debugger and code reviewer to resolve critical issues and ensure maintainable, high-quality code.}
\resumeItem{Contributed to the team's 2nd Place finishes at the RoboCup China Tournament (2023, 2024).}
\resumeItemListEnd

\resumeSubheading
{Core Member – SJTU Science and Technology Innovation Association (SSTIA)}{Oct 2023 – Present}
{Shanghai Jiao Tong University}{}
\resumeItemListStart
\resumeItem{Designed and hosted an internal workshop on Deep Learning for Robotics, introducing key concepts such as CNNs, object detection, and model deployment.}
\resumeItem{Mentored students in hands-on experimentation with PyTorch and simple generative models, strengthening team capabilities in AI integration.}
\resumeItem{Collaborated on interdisciplinary discussions linking perception modules with control systems.}
\resumeItemListEnd

\resumeSubheading
{Sponsorship Coordinator – Student Union, External Relations Department}{Oct 2023 – Present}
{Shanghai Jiao Tong University}{}
\resumeItemListStart
\resumeItem{Designed over a dozen posters and social media campaigns for various university events and competitions.}
\resumeItem{Helped establish the Integrated Media Center and authored event reports for notable student activities.}
\resumeItemListEnd

\resumeSubheading
{Student Representative – 2024 China-Arab Youth Development Forum}{Nov 2024}
{Shanghai International Studies University}{}
\resumeItemListStart
\resumeItem{Prepared and presented a simplified on-site demo with a scaled-down RoboCup setup under limited resources.}
\resumeItem{Engaged in dialogue with Arab leaders, showcasing the technological achievements of Chinese university students.}
\resumeItemListEnd



\resumeSubHeadingListEnd

\section{Awards \& Honors}
\resumeSubHeadingListStart
\resumeItem{2nd Place – RoboCup China Tournament (2023, 2024)}
\resumeItem{Best Design Award – 14th Li Ming Cup Mechanical Innovation Competition (2024)}
\resumeItem{Most Popular Award – SJTU GameJam Game Development Competition (2024)}
\resumeItem{Silver Medal – University Physics Competition (2023)}
\resumeItem{3rd Place \& Golden Globe Award – Lenovo Cup for Robot Football Strategy (2023)}
\resumeItem{2nd Prize – Shanghai Youth Science and Technology Innovation Competition (2021)}
\resumeItem{Finalist Award – Star of Tomorrow in Science and Technology (2021)}
\resumeSubHeadingListEnd

\end{document}
